The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2017-03-08 manuscript/manuscript.Rnw
fix a/an typo

Another annexin which is highly expressed in all term placentas is
\ac{ANXA5}, which was originally identified as a an anti-coagulant
protein, but is also involved in syncytium formation, membrane repair,
and reduction of spontaneous
abortion~\cite{Ueki.ea2012:Lossofmaternalannexin}. Other notable
syncytiotrophoblast fusion proteins, Syncytin-1 (\ac{ERVW-1}) and -2
(\ac{ERVFRD-1}) were not present in the core placenta, as they (or
genes similar to them) are not highly expressed in \dog, \bonobo, or \sheep,
nor was the Syncytin-2 receptor, \ac{MFSD2A} (\ac{FPKM} $\ge 10$
only in \human, \mouse, and \dog).

>>>>

Another annexin which is highly expressed in all term placentas is
\ac{ANXA5}, which was originally identified as an anti-coagulant
protein, but is also involved in syncytium formation, membrane repair,
and reduction of spontaneous
abortion~\cite{Ueki.ea2012:Lossofmaternalannexin}. Other notable
syncytiotrophoblast fusion proteins, Syncytin-1 (\ac{ERVW-1}) and -2
(\ac{ERVFRD-1}) were not present in the core placenta, as they (or
genes similar to them) are not highly expressed in \dog, \bonobo, or \sheep,
nor was the Syncytin-2 receptor, \ac{MFSD2A} (\ac{FPKM} $\ge 10$
only in \human, \mouse, and \dog).
